Hadoop Image Processing Framework

### 2015-03-15 Paper.tex
Everything but conclusion and related work.

The Hadoop Image processing framework provides transparency over two levels. The first level of transparency allows user to use the predefined MapReduce modules Downloader, Processor and Extractor for processing the image modules. The second of level of transparency allows the users to write custom map reduce programs as the framework is built in an hierarchal manner.

The great thing about Hadoop Image Processing framework is its built in such a way that using it is really simple. The framework strictly adheres java file writing and reading techniques and extends it to a new level of BundleFile Writing and Reading using hadoop framework. This makes user to work with hadoop image processing more flexible and easier. The main aim of the framework is to provide an abstractness in such a way that programming on a single computer is equivalent to programming on a hadoop cluster.  Listing 1. provides the similarities in code writing in java and image processing framework. Making framework similar to java helps understanding the framework more easier and reduces complexity. Listing 2 shows a sample code for setting image headers for processed images.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.45\textwidth]{files-chart2}
	\caption{Comparing File Writers and readers without and with using framework }
	\label{fig:files-chart}
\end{figure}

>>>>

The Hadoop Image processing framework provides transparency on
multiple levels.  Users can use the predefined MapReduce modules
(Downloader, Processor and Extractor) for processing the image
modules, and most image processing tasks require no more than this.
Users may also write custom MapReduce tasks within the framework,
taking advantage of its hierarchical construction.  This still
protects the user from the full complexity and error-prone nature of
the full Hadoop framework, but requires additional knowledge and
expertise on the user's part.

The Hadoop Image Processing Framework is intended to be extremely
simple to use. The framework strictly adheres to Java file writing and
reading techniques, extending those conventions to the Hadoop
framework's notion of reading and writing bundle files.  In this way,
working with Hadoop image processing is exactly like working on a
single system.  The main aim of the framework is to provide useful
software abstractions such that programming on a Hadoop cluster is
equivalent to programming on a single computer.  Listing 1
demonstrates the similarity between Java code written for a single
machine and the same code using the image processing framework.  The
framework's use of ordinary Java conventions helps in understanding
the software engineering process and reduces complexity.  Listing 2
demonstrates the mechanism for setting the image headers of processed
images.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.45\textwidth]{files-chart2}
  \caption{Comparing file writers and readers with and without using
    framework}
  \label{fig:files-chart}
\end{figure}
